\subsection{Technical and Managerial Lesson Learnt}
I learned a lot by doing this project . During the six months period I got to learn a vast number of technologies. These are lsited below :

\begin{itemize}
\item Operating system:\\
      Ubuntu
\item Languages used:\\
      Python, Html, CSS, JavaScript, PHP, Bash Scripting
\item Framework:\\
      Django 
\item Database:\\ 
      MySql
\item Typesetting by:\\ 
      LaTex
\item Designing:\\
      Gimp, Inkscape
\item Documenter:\\
      Doxygen
\item Code Maintainance:\\
      Github
\item ERP System:\\
      WebERP
\end{itemize}

So during this project I learned all the above things. Above all I got to know how Softwares are developed from the scratch. Planning, designing, developing code, working in a team, testing etc. These are all very precious things I got to learn during the training period
If I talk about the project, Automation project reduce lot of manual work . It has automated all the office work of TCC.  

\newpage
\subsection{Current status}
TCC Automation software is currently running in Testing and Consultancy Cell of our college and also on the experimental server of our college. I has automated all the manual work of TCC.
    Software has following applications in it:
\begin{itemize}
\item Login and registration
\item Register new client.
\item Search the client and add jobs for him or see the status.
\item Get different records of jobs based on type of work, type of report, payment type, type of lab etc.
\item Amounts get automatically summed up taking in account the sevice charges, income tax, sevice tax, education cess etc.
\item Online management.
\item As the database server is online so multiple clients can work on it.
\item Catalog feature.
\end{itemize}
\newpage 
\subsection{Future Scope}
Automation software reduces the manual work and save the money. It also reduces the man power and reduces the burden of handling lots of data. It keeps the backup of the record stored. As the project is complete but still there are many more things or areas
which can be added to the project to make that more reliable. These remaining areas may be:
\begin{enumerate}
\item Recieve the payment online through e-billing.
\item Managing the labs work through software, thus when there is any job that is to be done in a lab, they get email automatically.
\item Making it work like an ERP system i.e merge connect other departments also with, thus making it a big one.
\item SMS Service: When the work of a client is complete, the client and the employee should automaticlly receive a message regarding this.  
\item Report Fax: There may be an option through which the reports will be automatically faxed to the Clients/Employee.
\end{enumerate}


