\subsection{The Existing System}
\vskip 0.5cm
{\bf Introduction :}\\\\
The Software running today does all the entry and management of the Jobs, all done by Consultancy employees. The existing system manage the generation of Bill, Recipts and Vouchers very efficiently.\\\\
{\bf Limitations of Current System :}
\begin{itemize}
\item Currently, there is no central environment where the clients can register themselves online and order for a Job or can get information from and manage their own tasks. The existing system involves the employers of Consultacy Cell managing information by interacting directly with the clients about there Jobs.
\item Moreover, there is a need for a Search module that searches the previously registered Client, so that redundancy can be reduced to the maximum. 
\item Also the current Software requires the proper Normlisation of Database.
\item Apart from all these there is a need to make the calculation of total amount of Job done to be automated by Software itself. The current system requires the manual calculation. 
\item There is also a need of proper Developer Documentation.  
\item There should be a single click installation procedure for the Software.
\item Reports are not generated in the Software.
\end{itemize}

\newpage
\subsection{Software Functions Provided in Proposed system}
\vskip 0.5cm
\begin{description}
\item[Registeration \& Login] :\\
The software user would be required to Register through a screen. After authentication and login he would be able to access only those areas for which he is capable to access.
\item[Administrator Maintenance] :\\
Administrator can add or update the details, and also can see information of all employees and can see his or her information. New Database table information can also be added.
\item[Employee Maintenance] :\\
As employees are directly related to clients, so they are able to add or update the details of clients using this section. Admin can see all the clients. Employees can manage their clients only.
\item[Client Maintenance] :\\
Clients are the end users that benefit from the TCC Automation Software. A client can get information of all the available work done in Testing & Consultancy Cell also apply for same. They can also view the status of there previous works done in the Cell.
\item[Catalog] :\\
Using the Catalog, the clients can get an estimate of price for all the tests done in the Cell. Catalog lists down all the works done in the Cell.
\item[Cart] :\\
Using this functionality, a client can test multiple materials in a single Job, thus getting only one Receipt and Bill for a Job.
\item[Report Generation] :\\
The Report generation for a material tested is made easier now. The reports generated can then be downloaded in pdf format and then can be given to the repective clients.
\end{description}




